Untitled

### 2020-11-20 ms/manuscript.Rmd
Update MS
add function to print p-value from t-test results

```{r load-data}
loadd(
  list = c(
    "climate",
    "filmy_species",
    "moorea_sites",
    "phylosig",
    "range_types",
    "recovery_species_means"
  )
)
```

@@

# Vector of species that I know *after* running the t-test have significant
# differences and discuss in the MS.
species_with_signif_dt_diff <- c("Hymenophyllum_polyanthos", "Hymenophyllum_digitatum", "Crepidomanes_minutum2", "Polyphlebium_endlicherianum", "Polyphlebium_borbonicum")

t_test_results %>% 
  filter(response == "recover", p_value < 0.05) %>%
  # Make sure that species with signif diff in DT mentioned
  # in MS match those in the actual analysis results
  verify(setequal(.$species, species_with_signif_dt_diff)) %>%
  select(species, estimate, p_value) %>%
  arrange(p_value)

@@

Gametophytes of low elevation epiphytes had the highest DT (ca. 80% recovery), followed by high elevation epiphytes and saxicolous species (both with recovery from ca. 25% to 75%), with terrestrial species essentially non-tolerant (less than 20% recovery; Fig. 5).
DT of gametophytes did not significantly exceed that of sporophytes for any species except for saxicolous *P. endlicherianum* (Fig. 5; *t*-test, *P* = 0.012), and was significantly lower in gametophytes than sporophytes of some high elevation epiphytic species including *C. minutum* var. 2, *H.* *digitatum*, *H. polyanthos*, and *P. borbonicum* (Fig. 5; *t*-test, *P* = 0.0093, *\<*0.001, *\<*0.001, 0.012, respectively).

>>>>

```{r load-data}
loadd(
  list = c(
    "climate",
    "filmy_species",
    "moorea_sites",
    "phylosig",
    "range_types",
    "recovery_species_means",
    "t_test_results"
  )
)
```

@@

# Make helper function to check on p-value significance and extract from t_test_results
#
#' @param species_select Name of species to select from t-test results
#' @param response_select Name of response to select from t-test results
#' @param data t-test results
#' @param p_check Boolean: should the p-value be required to be less than 0.05?
#'
#' @return A p-value for the selected species and response
ttest_pval <- function(species_select, response_select, data = t_test_results, p_check = TRUE) {
  data %>% 
    # Filter to appropriate species and response
    filter(species == species_select, response == response_select) %>%
    # Verify the p-value is significant (or override with `p_check = FALSE`)
    assert(function (x) magrittr::is_less_than(x, 0.05) | !p_check, p_value) %>%
    # Format the p-value
    mutate(
      p_value = case_when(
        p_value < 0.001 ~ "<0.001",
        TRUE ~ jntools::round_t(p_value, digits = 3))
    ) %>% 
    pull(p_value)
}
```

@@

Gametophytes of low elevation epiphytes had the highest DT (ca. 80% recovery), followed by high elevation epiphytes and saxicolous species (both with recovery from ca. 25% to 75%), with terrestrial species essentially non-tolerant (less than 20% recovery; Fig. 5).
DT of gametophytes did not significantly exceed that of sporophytes for any species except for saxicolous *P. endlicherianum* (Fig. 5; *t*-test, *P* = `r ttest_pval("Polyphlebium_endlicherianum", "recover")`), and was significantly lower in gametophytes than sporophytes of some high elevation epiphytic species including *C. minutum* var. 2, *H.* *digitatum*, *H. polyanthos*, and *P. borbonicum* (Fig. 5; *t*-test, *P* = `r ttest_pval("Crepidomanes_minutum2", "recover")`, `r ttest_pval("Hymenophyllum_digitatum", "recover")`, `r ttest_pval("Hymenophyllum_polyanthos", "recover")`, and `r ttest_pval("Polyphlebium_borbonicum", "recover")`, respectively).
